---
title: "Walk_aurant_ify"
author: "MercedeszLehoczky"
date: "2023-04-28"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Introduction

This project is the final capstone project for the University of Lucerne FS23 "Data Mining in R" course.
The purpose of this project was to gain insights into data mining methods and to create an original project using the freshly learned skills.

## Idea
The project is meant to be an idea for a "self-care" walk. 
The user would access their Spotify account, choose a playlist, and the project matches the length of their playlist to a restaurant in Lucerne. The starting point is always the University of Lucerne and the route is calculated via walking.

For this, Spotify API, Google Places API and Google Directions API are used.


```{r cars}
summary(cars)
```

## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
