---
title: "Walk_aurant_ify"
author: "MercedeszLehoczky"
date: "2023-04-28"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Introduction

This project is the final capstone project for the University of Lucerne FS23 "Data Mining in R" course.
The purpose of this project was to gain insights into data mining methods and to create an original project using the freshly learned skills.


## Idea
The project is meant to be an idea for a "self-care" walk. 
The user would access their Spotify account, choose a playlist, and the project matches the length of their playlist to a restaurant in Lucerne. The starting point is always the University of Lucerne and the route is calculated via walking.

For this, Spotify API, Google Places API and Google Directions API are used.


##Initialisation

From the user end, the user needs to create a Spotify app on <https://developer.spotify.com/> and have their "Client ID" and "Client secret" ready.
Furthermore, their Spotify User ID will also be needed.

For Google API, get an API key from <https://developers.google.com/maps/>. 
Kindly consult the documentations for more precise information.

The scripts ask for the keys password-style, however, it is recommended to create a "keys.csv" file in the "data" folder to store these keys for the shiny application. The format is the following:
api_id            | api_key
spotify_id        | xxx         #client ID
spotify_secret    | xxx         #client secret
spotify_user      | xxx         #user ID
google_id         | xxx         #Google API key



### Let's see the playlists

After initialisation, the first script ("01_Spotify_playlists.R") is ran and the first important output is the names of playlists scraped.

There are issues with the functions used here. In the package "spotifyr", there are multiple great tools, but the function "get_user_playlists" is limited to 50 playlists, usually displaved as latest addition to oldest. It includes saved playlists from others too.

The goal is to scrape the length of the playlists, saved in seconds. Another issue is, that not all playlists are available for getting their length ( and track list, etc). This could be because of the playlist not being public or being owned by someone else.

```{r}
my_plists$name
```

## Restaurants

Next, the restaurants from Lucerne are scraped using the Google Places API ("02_Places_API.R").

The issue here is that the API only lets us scrape 20 restaurants at a time. 
The other issue is that scraping places tagged as restaurants will also scrape other establishments, such as hotels, since usually there are many tags in the 'types' section (like hotels, bars, some gyms, etc). 

```{r}
places
```

## Routes

Then, the walking routes to each location (restaurant) are scraped via Google Directions API ("03_Directions_API.R"). The same API key can be used for this and script 02. The list og endpoints are given from the scraped table created in script 02.

```{r}
route_info
```



